---
title: "P8105_hw6_REN XIN"
output: github_document
date: "2022-11-30"
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
library(rvest)
library(viridis)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 6, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

###Problem 1:


###Problem 2:

##Step 1: import the data.
```{r}
homicides_df = read_csv("data/homicide-data.csv",na = c("", "NA", "Unknown"))
homicides_df
```

##Step 2 :Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL
```{r}
homicides_df = homicides_df %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  filter(
    !city_state == c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"),
    victim_race == c("White", "Black")
  ) %>% 
  mutate(
    victim_age = as.numeric(victim_age),
    homicide_solved = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1
    )
  ) %>%
  select(city_state, homicide_solved, victim_age, victim_sex, victim_race)

homicides_df
```

Description：I filtered 5 variables as col according to the requirements, they are city_state, homicide_solved, victim_age, victim_sex, victim_race. This table has 19,893 entries and 5 total columns.

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_df =
  homicides_df %>%
    filter(city_state == "Baltimore, MD")
  glm(
    homicide_solved ~ victim_age + victim_race + victim_sex,data = baltimore_df,family = binomial()) %>%
  broom::tidy()
  
```

